Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-12-06 referee_2.tex
Fixing minor errors. Added statement about fixing Figure 7. Final versions to be submitted.

\begin{referee}
    -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding. I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding. Maybe it has to do with the scaling of the H2 fraction?  It is important to know how the authors scale the H2 fraction as a function of radius for different halo masses (see point above). If this is not the reason, please explain what else is causing more massive haloes to be worse at self-shielding.  
\end{referee}
    We thank the reader for asking these questions. They have caused us to go back to our calculations to try to find the source of the increase in the shielding factor for larger halo masses. It turned out that there was an error in our calculations stemming from when we assumed a constant H2 fraction. This has been fixed, as well as an incorrect decimal place in our core radius calculations, and we now see decreased shielding factors (more effective shielding) for increased halo masses, as expected. We would like to remind the referee that the dashed lines indicate a smaller core radius, and thus, the shielding factor is even more effective for this core radius since more H2 is being added to the column density.

@@

\begin{referee}
    - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}
    We have added a panel to the left of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.

    The limits from Schauer+19 have been added to the left panel of Figure 10, and the previous description regarding the 21cm signal has been removed. Their citation has been added to the list of citations investigating streaming velocities.

    We have added a short comparison to Hirano+17 (Science) and Schauer+19 have also added their citation to the list of citations mentioned previously.

@@

	The sentence "Often in the literature, streaming velocities are only studied for a few haloes" has been removed.

\end{document}

>>>>

\begin{referee}
    -- Compared to the previous version with a constant profile, the shielding factor increases for higher halo masses (in the previous version of the paper, there was a slight decrease): leading to less shielding. I do not understand where this is coming from, a more massive halo has a larger overall gas mass, and therefore more H2 and more shielding. Maybe it has to do with the scaling of the H2 fraction?  It is important to know how the authors scale the H2 fraction as a function of radius for different halo masses (see point above). If this is not the reason, please explain what else is causing more massive haloes to be worse at self-shielding.  
\end{referee}
    We thank the referee for asking these questions. They have caused us to go back to our calculations to try to find the source of the increase in the shielding factor for larger halo masses. It turned out that there was an error in our calculations stemming from when we assumed a constant H2 fraction. This has been fixed, as well as an incorrect decimal place in our core radius calculations, and we now see decreased shielding factors (more effective shielding) for increased halo masses, as expected. We would like to remind the referee that the dashed lines indicate a smaller core radius, and thus, the shielding factor is even more effective for this core radius since more H2 is being added to the column density.

@@

\begin{referee}
    - The authors put their work in comparison to Schauer+19, ApJL 877, 5 who match the star formation efficiency in minihaloes to the observed 21cm signal. They should rather compare to Schauer+19 MNRAS, 484, 3510 who performed cosmological hydrodynamical simulations for the minimum and average halo mass in different streaming velocity regions. Please include their limits in your Figure 10, as done with the Naoz+13 results, and a short comparison to Hirano+18 (their Science paper). Please include these references also in the introduction. Also the sentence "Often in the literature, streaming velocities are only studied for a few haloes" seems outdated.
\end{referee}
    We have added a panel to the right of Figure 10 to de-clutter the main figure and to separate the halo mass ranges and minima related to streaming velocities.

    The limits from Schauer+19 have been added to the right panel of Figure 10, and the previous description regarding the 21cm signal has been removed. Their citation has been added to the list of citations investigating streaming velocities.

    We have added a short comparison to Hirano+17 (Science) and Schauer+19. We have also added the Hirano+17 citation to the list of citations mentioned previously.

@@

	The sentence ``Often in the literature, streaming velocities are only studied for a few haloes" has been removed.

    We also want to point out that the right panel of Figure 7 has been adjusted to represent the data in a clearer way. The y-axis bins have been centered on integers, and the median red line is now centered on those bins. 
\end{document}
